Completing a PhD will be one of the most fulfilling moments in my life. Though
there were countless moments that I doubted I would finish, I was able to
persevere because of the support of many colleagues, friends, and family. I will
always be grateful for their support.

I would first like to acknowledge my biggest advocates: my parents. My entire
academic life, from undergrad until now, has been filled with struggles and
achievements, doubts and confidence, lows and highs. From failing my first
semester in university, to my graduation today, my parents have given me
unwavering support, unconditional compassion, and their unbreakable confidence in
me. I could never have persisted until the end of my PhD without the foundation
they provided me. I am forever grateful to them.

During my PhD, I was also incredibly lucky to have a new advocate and family
member entire my life: my wonderful wife Yixue Zhao. Her love and support
compares only to my parent's. No one in my life has more persistently provided me
with words of encouragement, and built my confidence than she. Her passion for
life and positive vibes helped me overcome some of the lowest lows throughout my
PhD. She has taught me many lessons, not only on how to be a better researcher,
but also on how to live a happy and meaningful life.

Next, I would like to acknowledge my advisor Chao Wang's support and many
contributions to this dissertation. Throughout my PhD, Chao taught me many
valuable lessons about both the theory and practice of formal methods, and about
doing research in general. In addition, during my many struggles, especially in
the beginning of my PhD, he struggled with me, and did not give up. My first
project took nearly two years of effort -- far longer than the average project in
our group. Throughout this time, I asked many naive questions, made many
mistakes, and at times I went months without making progress, but Chao was always
there struggling with me. I learned many invaluable lessons working with Chao
that I will carry with me throughout the rest of my career. I would also like to
thank him for the many thought-provoking and productive discussions we had, which
uncovered the interesting problems and solutions that make up the contributions
of this dissertation.

I would also like to thank those who served on my dissertation committee, namely
Jyotirmoy Deshmukh, Murali Annavaram, Nenad Medvidovic, William G.J. Halfond, and
Bhaskar Krishnamachari. I'd like to thank them for their time serving on my
committee, for their thought-provoking questions, and feedback on my
presentations. I'd also like to thank Jyotirmoy for his interesting discussion,
ideas for future work, and for being an excellent collaborator. I hope we can
continue our collaborations in the future.

Next, I would especially like to thank my Master's program advisor, Peter
Peterson. Peter played a pivotal role in getting me into the PhD program at USC.
I have fond memories of his computer security course, the genuine passion that
went into his lectures and course material, and the one-of-a-kind learning
environment he was able to create. This course helped me discover my passion for
academics and learning, which motivated me to apply to a Master's program, and
eventually a PhD program. In addition, during the Master's program, Peter was
extremely supportive of my academic pursuits. He helped me find an interesting
thesis project, connected me with other researchers which lead to a summer
internship, guided me through PhD application, and so much more that I can't name
them all.

I also had many friends who supported my journey into the PhD program. I'd like
to thank Laura Krebs for being a wonderful friend, a role model student, and for
believing in me during my undergrad and Master's program. If it were not for her
pushing me to achieve excellence during my undergrad, I would never have made it
into the Master's or PhD program. I'd also like to thank the many friends I made
during the Master's program for the wonderful memories that made the program
truly special. I remember fondly the many games of Settlers of Catan played with
Jonathan Beaulieu and Xinru Yan, the countless hours spent rock climbing with
Paul ``The Wall'' Vaynshenk, and the horribly cringy ``Saviors of the Servers''
costumes that Ankit Gupta and I concocted one bored Halloween night.

I'd also like to thank the many friends I made during the PhD program who
supported me. My labmates Jingbo Wang, Tianqin Zhao, Chungha Sung, Farmer Daniel
Guo, Meng Wu, Zunchen Huang, Yannan Li, Chenggang Li, and the colleagues from my
neighboring labs Adriana Sejfia, Marc Juarez, Paul Chiou, Nikola Lukic, Daye Nam,
Yinjun Lyu, and Mian Wan helped make my PhD and enjoyable experience.

% Derek and Paul
Finally, I would like to thank those close friends and family who have supported
me both throughout this journey, and my life as a whole. I'd like to thank my
closest friends Derek Paulsen, Paul Vaynshenk, Jonathan Beaulieu, and Xinru Yan.
Your friendship brings invaluable joy to my life.
